stupid backoff

### 2019-11-30 al_stup.Rmd
shiny app
server code with rds

```{r}
library(quanteda)
library(dplyr)
library(stringr)
library(readtext)
library(spacyr)
library(ggplot2)
library(wordcloud)
library(data.table)
```

@@

#takin 15% of data for memory reasons
set.seed(1)
x = sample(2360148, 350000, replace = F)

>>>>

```{r}
library(quanteda)
library(dplyr)
library(stringr)
library(wordcloud)
library(data.table)
library(readtext)
library(spacyr)
library(ggplot2)

@@

#takin 15% of data for memory reasons
set.seed(1)
x = sample(2360148, 590037, replace = F)
